---
title: "R語言code整理"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1. Introduction


## (1) Calculator
```{r}
5 + 3

5 * 3

5 / 3

5 ^ 3

5 %% 3

5 %/% 3

```
## (2) Sequence
```{r }
1:10

seq(1, 10, 2)

seq(1, 10, length.out = 6)
```
## (3) Basic features
We tell R to make the assignment using an arrow “<-”. R also supports
using “=” in most circumstances. However, “<-” is recommended as it
makes clear that we are requesting an assignment, rather than stating a
relation.
```{r}
a <- 3 ^ 5
b = 3 ^ 5
a

b
```
## (4) Special values in R
Missing value, Not a Number, Infinity, π, and 10^−3:
```{r}
NA

NaN 

Inf 

-Inf 

pi

1e-3
```
## (5) R us not just an calculator
There are a lot of functions you can use. Let’s see some related to Statistics.


Descriptive statistics:
```{r}

x <- 1:25

mean(x)

var(x)

median(x)

quantile(x, c(0.1, 0.5, 0.7))

x <- c(1:25, NA)
summary(x)
```

# 2. Vectors

## (1) Numeric vector
```{r}
vt1 <- c(1:5)
vt2 <- c(3:6)
vt2 <- c(vt2, vt1)
vt2
```
Use “seq()” and “rep()” to construct a vector with similar patterns
```{r}
seq(1, 5, by = 0.5)

seq(1, 10, length.out = 5)

rep(3, 12)

rep(seq(2, 10, 2), 2)

```
創建null vector，再進行迭代
```{r}
a <- c(3, 5, 9, 10)
b <- c(14, 15, 17)
V1 <- c()
V1 <- c(V1, a, b) 
V1
```
When to use “c( )” and when to use a vector with known length?
c( ): Easy to add a value into the vector; need not know the length.
rep(NA, n): With known length and the position of elements.


###  elements in the vector
*Use “unique( )” to return the elements that appear at least one time.


*Use “table( )” to count the number of each element from the vector.
```{r}
b <- c(3, 3, 3, 3, 5, 5, 1, 2, 10, 10, 8)

unique(b)

table(b)
```
Sorting and ordering of a vector
```{r}
a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11)
sort(a)

sort(a, decreasing = TRUE)
```
change values in a vector&Deleting elements from a vector
```{r}
a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11)
a[5] <- -3
a[8] <- -1
a
vt1
vt1[-2]
## [1] 1 3 4 5
```
## (2) Character vectors
```{r}
"Hello World!!!"

print("Hello R World!!!")

```
*Character vector: the vector is made up of strings of characters.


*All elements of a vector must be of the same type.
```{r}
colors <- c("red", "yellow", "BLUE")
more.colors <- c(colors, "green", "cyan")
more.colors
##An attempt to mix data types in a vector
z <- c("red", "green", 12)
z
```
Basic operations for character vectors
```{r}
y.in.V <- grep("y", more.colors)
e.in.V <- grep("e", more.colors)
more.colors[y.in.V]
more.colors[e.in.V]
E.in.V <- grep("E", more.colors)
more.colors[E.in.V]
```
-To building up strings, use “paste()”.
```{r}
paste(colors, "line") ## with space

paste(colors, "line", sep = "" ) ## no space

## use ";" to seperate strings
paste("I like", colors, collapse = "; ")
```

## (3) Logical vectors
TRUE and FALSE are reserved words denoting logical constants in the R,


whereas T and F are global variables whose initial values set to these.
```{r}
TRUE

FALSE

T

F
```
Binary operators which allow the comparison of values in atomic vectors (relational
operators).


Number: Compare 3 and 5


“==”: equal


“!=”: not equal
```{r}
c(3 < 5, 3 > 5)

c(3 <= 5, 3 >= 5)

3 == 5

3 != 5
```
Compare the same location of elements individually.
```{r}
B <- c(3, 1, 5, 4, 7); C <- c(23, 1, 44, 5, 3)
B == C

D <- c(2, 5 ,6, 10)
B == D
```
###  “is.” series
“is.XYZ()” is any comparison to the type “XYZ” of an object.

is.null()

is.na()

is.nan()

is.infinite()

is.character()

is.integer()

is.numeric()
```{r}
is.null(c())

c(is.na(NA), is.na(2))
```

```{r}
x1 <- 1:5
x2 <- c(1:3, 2.2)
x3 <- colors
c(is.integer(x1), is.numeric(x1), is.double(x1))

c(is.integer(x2), is.numeric(x2), is.double(x2))

c(is.character(x3), is.numeric(x3))
```
Use “class( )” to identify the type of a vector.

```{r}
a <- c(3, 4, 2, 7)
b <- c("red", "yellow", "blue")
c <- c(TRUE, FALSE)
c(class(a), class(b), class(c))

c(class(2), class(2.0), class(as.integer(2)))
```
# 3. Matrix

## (1) Constrct a matrix by row & column
```{r}
#by row
a <- 1:5; b <- 6:10;
c <- 11:15; d <- 16:20;
M1 <- rbind(a, b, c, d)
M1
#by column
M2 <- cbind(a, b, c, d)
M2
dim(M1)
dim(M2)
```
## (2) Constrct a matrix by longer vector
```{r}
X <- 1:20
matrix(X, nrow = 4, ncol = 5)
matrix(X, nrow = 4, ncol = 5, byrow = TRUE)
```
### Features for a matrix
```{r}
M1

dim(M1)

colnames(M1); rownames(M1);

colnames(M1) <- c("V1", "V2", "V3", "V4", "V5")

dimnames(M1)

dimnames(M2)

```
### Extract elements from a matrix
```{r}
M1

M1[5] 

M1[13] 

```
Recall M1. The names of rows are a, b, c, and d. Take the rows of b and c

The names of columns are V1, V2, V3, V4, and V5. Take the rows of b and
c and the columns of V2 and V5.

```{r}
M1[c("b", "c"), ]

M1[c("b", "c"), c("V2", "V5")]
```
### simple calculation of matrix
Note: Use **%*%** to evaluate multiplication of matrices
```{r}
A <- matrix(c(1:4), 2, 2)
A + 3
A - 1
A * 5
A / 4

B <- matrix(c(5:8), 2, 2)
A + B
A * B
#summary statistics
C <- matrix(1:9, 3, 3)
colSums(C)

rowSums(C)

colMeans(C)

rowMeans(C)

A %*% B

```
Tranpose,Diagonal & Determinat
```{r}
t(A)

t(C)

diag(A)

diag(B)

det(A)

det(B)
```

# 4. Control Flow
## (1) The for loop
When to use?
See patterns of behaviour, not just a single instance.
The for() statement allows one to specify that a certain operation
should be repeated a fixed number of times.
### Example:
Construct a vector as
Xn+1 = 2Xn + 3,
where X0 = 3, n = 1, 2, 3, 4, 5, 6, 7.
```{r}
vec.X.v1 <- c()
Xn <- 3
for(n in 1:7){
Xn <- 2*Xn + 3
vec.X.v1 <- c(vec.X.v1, Xn)
}
vec.X.v1
```
Evaluate n!

n! = n ∗ (n − 1) ∗ (n − 2) ∗ · · · ∗ 2 ∗ 1.
Try n = 10.
```{r}

n <- 10
ans <- 1
for(j in n:1){
ans <- ans * j
}
ans
factorial(n)

```
For loop in matrix

evaluate the mean for each row.
```{r}

A <- matrix(c(3, 2, 1, 2, 2, 6, 4, 1,
4, 8, 6, 2, 5, 10, 8, 6,
3, 4, 3, 4), 4, 5)
nr <- dim(A)[1]
m <- c()
for(j in 1:nr){
m <- c(m, mean(A[j, ]))
}
m
```
## (2) The if statement 
Try to find the locations of NA

Given C = {3, 5, NA, 12, 0.2, NA, −2}, find the locations of NA.
```{r}
C <- c(3, 4, NA, 12, 0.2, NA, -2)
for(i in 1:7){
if(is.na(C[i])) print(i)
}

```
Count the number of each class
```{r}
basket <- c("r", "b", "y", "y", "y", "r", "r", "b")
n.r <- 0; n.b <- 0; n.y <- 0
for(i in 1:length(basket)){
if(basket[i] == "r"){
n.r <- n.r + 1
}else if(basket[i] == "b"){
n.b <- n.b + 1
}else{
n.y <- n.y + 1
}
}
c(n.r, n.b, n.y)
```
Re-assign the value to the class

Let “r” be 1, “b” be 2, and “y” be 3
```{r}
v.basket <- rep(NA, length(basket))
for(i in 1:length(basket)){
if(basket[i] == "r"){
v.basket[i] <- 1
}else if(basket[i] == "b"){
v.basket[i] <- 2
}else{
v.basket[i] <- 3
}
}
v.basket

```
ifelse(condition, commands when TRUE, commands when FALSE)
Let “r” be 1, “b” be 2, and “y” be 3
```{r}
v.basket <- ifelse(basket == "r", 1, ifelse(basket == "b", 2, 3))
v.basket
```

## (3) The  while loop
The pattern of repetition isn’t known in advance and we need to do some
calculations and keep going as long as a condition holds. The
while()statement accomplishes this.

### Relationship between for() and while()
*while(): Need the initial, condition of stopping, and iteration or
replacement
```{r}
for(j in 1:8){
print(j)
}

j <- 1
while(j <= 8){
print(j)
j <- j + 1
}
```
Flip a coin
```{r}
coin <- c(0, 0, 0, 0, 0, 0, 1, 0, 1, 0, 1, 0,
1, 1, 0, 1, 1, 0, 0, 0, 1, 0, 1, 0,
0, 0, 0, 0, 0, 0, 1)
N <- c(); j <- 1
while(j <= length(coin)){
n.fail <- 0
while(coin[j] != 1){
n.fail <- n.fail + 1
j <- j + 1
}
N <- c(N, n.fail + 1)
j <- j + 1
}
N
```
### break,repeat and next
*break

if (condition) break

The break statement causes the loop to terminate immediately. break statements

can also be used in for() and while() loops.


*repeat

Use “repeat” to repeat until we execute a break statement.

repeat { statements }

This causes the statements to be repeated endlessly.


*next:

The next statement causes control to return immediately to the top of the loop; it

can also be used in any loop.

***我們利用Fibonacci numbers to demo

List all Fibonacci numbers less than 100. Use for() and if(condition) break.
```{r}
Fib1 <- 1
Fib2 <- 1
Fibonacci <- c(Fib1)
for(j in 1:1000){
if(Fib2 < 100){
Fibonacci <- c(Fibonacci, Fib2)
Fib1 <- Fibonacci[length(Fibonacci) - 1]
Fib2 <- Fib1 + Fibonacci[length(Fibonacci)]
}else{
break
}
}
Fibonacci
```
List all Fibonacci numbers less than 100. Use repeat{ } and break.
```{r}
Fib1 <- 1
Fib2 <- 1
Fibonacci <- c(Fib1)
repeat
{
if(Fib2 < 100){
Fibonacci <- c(Fibonacci, Fib2)
Fib1 <- Fibonacci[length(Fibonacci) - 1]
Fib2 <- Fib1 + Fibonacci[length(Fibonacci)]
}else{
break
}
}
Fibonacci

```
List all Fibonacci numbers less than 100. Use repeat{ } and next.
```{r}
Fib1 <- 1
Fib2 <- 1
Fibonacci <- c(Fib1)
for(j in 1:100){
if(Fib2 >= 100) next
Fibonacci <- c(Fibonacci, Fib2)
Fib1 <- Fibonacci[length(Fibonacci) - 1]
Fib2 <- Fib1 + Fibonacci[length(Fibonacci)]
#print(j)
}
Fibonacci
```
# 5. Functions
## (1)print( ) & cat( )
print( ) shows with " " between characters.
cat() shows without " " between characters. You can add ”\n" to make
characters in a new line.
```{r}
x <- c("A", "B", "C", "D")
print(x)

cat(x)

cat(x[1], "\n",
x[2], "\n", sep = "" )
```
## (2)function( )

Use function( ) when you only have one main code for evaluation and
multiple possible input, like

f (x) = 3x + 2, x = 2, 3, 4.

f means a name of a function of input x when x = 2, 3, 4
```{r}
f <- function(x){
3*x + 2
}
f(2); f(3); f(4)
```
examples:
```{r}
make.percent <- function(x){
x.percent <- round(100*x, digits = 1)
x.show <- paste(x.percent, "%", sep = "")
cat(x.show)
}
make.percent(c(0.8933, 0.2344, 0.0764, 0.7736))

```
You must tell what will be return when you use the function by return( ) or
invisible( ). If you don’t put return( ) at the end of the function, it will
treat the last line as the result automatically
```{r}
f <- function(x){
return(3*x + 2)
}
f(2)

f <- function(x){
res <- 3*x + 2
}
f(2)
a <- f(2); a
```
### Functions for multiple input variables
Use function( ) when you only have one main code for evaluation and

multiple possible input, like

f (x, y) = x^2^ +y^2^

x, y = 2, 3, 4.

f means a name of a function of input x and y when x, y = 2, 3, 4.
```{r}
f <- function(x, y){
x^2 + y^2
}
f(2, 2); f(2, 3); f(2, 4)
```
examples
```{r}
make.percent <- function(x, x.digits){
x.percent <- round(100*x, digits = x.digits)
x.show <- paste(x.percent, "%", sep = "")
return(x.show)
}
make.percent(c(0.8933, 0.2344, 0.0764, 0.7736), 0)

make.percent(c(0.8933, 0.2344, 0.0764, 0.7736), 1)

make.percent(c(0.8933, 0.2344, 0.0764, 0.7736), 2)
```
### Use function and return multiple outputs

list( ) is a collection of multiple types of objects, like vectors, characters, numbers,

Example:
```{r}
X <- list(a = 3, b = c(1,2,3,4,5), c = c("A", "B"))
X
```
Use $ or  [ [ ] ]

$: the name of the element.    [ [ ] ]: the location or the name of the element.

```{r}
X <- list(a = 3, b = c(1,2,3,4,5), c = c("A", "B"))
X$a

X[[2]]

X[["c"]]
```
Use function( ) and list( )
```{r}
perfect.number <- function(a, b){
k <- a
res <- c()
ans <- list()
while(k < b){
fac <- c()
for(j in 1:k){
if((k %% j) == 0) fac <- c(fac, j)
}
if(k == sum(fac[-length(fac)])) {
res <- c(res, k)
ans[[paste(k)]] <- fac[-length(fac)]
}
k <- k+1
}
ans$number <- res
return(ans)
}
```
Output: perfect number
```{r}
Ans <- perfect.number(1, 100)
Ans

```
# 6. Related to data
## (1)data.frame( )

*Most data sets are stored in R as data frames.

*These are like matrices, but with the columns having their own names.

*Columns can be of different types from each other.

Use the data.frame() to construct data frames from vectors:

example:
```{r}
colors <- c("red", "yellow", "blue")
numbers <- c(1, 2, 3)
colors.and.numbers <- data.frame(colors, numbers,
more.numbers = c(4, 5, 6))
colors.and.numbers
```

### Difference from a matrices
These are like matrices, but with the columns having their own names.

Columns can be of different types from each othe

```{r}
X <- matrix(NA, 3, 3)
X[,1] <- c("red", "yellow", "blue")
X[,2] <- c(1, 2, 3)
X[,3] <- c(4, 5, 6)
colnames(X) <- c("colors", "numbers", "more.numbers")
X
```
Use str() to examine the types of columns in the data frame.
```{r}
str(colors.and.numbers)
colors <- c("red", "yellow", "blue")
numbers <- c(1, 2, 3)
colors.and.numbers <- data.frame(colors, numbers,
more.numbers = c(4, 5, 6),
stringsAsFactors = FALSE)
str(colors.and.numbers)
```
More on data.frame(): add rows
```{r}
data1 <- data.frame(colors, numbers, more.numbers = c(4, 5, 6),stringsAsFactors = FALSE)
data1 <- rbind(data1, c("black", 3, 5))
data1
```
More on data.frame(): add columns
```{r}
colors <- c("red", "yellow", "blue")
number1 <- c(1, 2, 3)
number2 <- c(10, 11, 12)
colors.and.numbers <- data.frame(colors, number1) ## construct data.frame
colors.and.numbers$more.numbers <- c(4, 5, 6) ## add one column
colors.and.numbers <- cbind(colors.and.numbers, number2) ## add one column
colors.and.numbers
```

# 7. Graphics
## Statistical Figure
Given an arbitray vector x:

1 Histogram: hist(x)

2 Boxplot: boxplot(x)

3 Density plot: plot(density(x))
```{r} 
x.norm <- rnorm(100, mean=0, sd=1)
hist(x.norm)
```

```{r}
boxplot(x.norm) 

plot(density(x.norm))
```


For discrete variables x:

1 Barchart: barplot(x)

2 Piechart: pie(x)
```{r}
x <- sample(c(1:8), 100, replace=TRUE, prob=c(8:1))
x <- table(x)
names(x) <- c("A", "B", "C", "D", "E", "F", "G", "H")
barplot(x)
```

```{r}
pie(x)
```
Scatter plot is for the correlation between two variables.
Use plot(x, y)
```{r}
x <- rnorm(100)
y <- 3*x + rnorm(100, 0, 1)
plot(x, y)

cor(x, y)
```
### General plot function: plot(. . . )
plot(x, y,
type = "p", ### types of the plot
pch = , ### the symbol in the plot
main = NULL, ### the title of the plot
lty = , ### the style of a line
lwd = , ### the width of a line
cex = , ### the size of an text
bty="o", ### the box around the plot
col = , ### the color of an object
xlim = NULL, ylim = NULL, # the range of an axis
sub = NULL, ### the sub-title of the plot
xlab = NULL, ylab = NULL, # the name of an axis
cex.main = ### the size of the title
)

## ggplot2 額外介紹
```{r}
library(ggplot2)
library(dplyr)
library(gapminder)
#散佈圖
#範例1
data("mpg")
mpg %>% head
canvas<-ggplot(mpg,mapping=aes(x=cyl,y=cty))
canvas #加畫布
e <- ggplot(mpg, aes(cty, hwy))
e + geom_point()
#範例2
gapminder_2007 <- gapminder %>%filter(year == 2007)
scatter_plot <- ggplot(gapminder_2007, aes(x = gdpPercap, y = lifeExp)) +
  geom_point()
scatter_plot
#線圖
north_asia <- gapminder %>%filter(country %in% c("China", "Japan", "Taiwan", "Korea, Rep."))
line_plot <- ggplot(north_asia, aes(x = year, y = gdpPercap, colour = country)) +geom_line()
line_plot

#直方圖
hist_plot <- ggplot(gapminder_2007, aes(x = gdpPercap)) +geom_histogram()
hist_plot
#調整bin
hist_plot2 <- ggplot(gapminder_2007, aes(x = gdpPercap)) +geom_histogram(bins = 20)
hist_plot2

#盒鬚圖
#單看一個數據
box_plot <- ggplot(gapminder_2007, aes(x = 0,y=gdpPercap)) +geom_boxplot()
box_plot
#交叉比對
box_plot <- ggplot(gapminder_2007, aes(x = continent, y = gdpPercap)) +
  geom_boxplot()
box_plot

#長條圖
gdpPercap_2007_na <- gapminder %>%filter(year == 2007 & country%in%c("China", "Japan", "Taiwan", "Korea, Rep."))
bar_plot <- ggplot(gdpPercap_2007_na, aes(x = country, y = gdpPercap)) +
  geom_bar(stat = "identity")
bar_plot

#建立樣本
ice_cream_flavor<-rep(NA,100)
for(i in 1:100){
  ice_cream_flavor[i]<-sample(c("vanilla","chocolate","matcha","other"),size=1)
}
ice_cream_df<-data.frame(ice_cream_flavor=ice_cream_flavor)

flavor<-names(table(ice_cream_flavor))
votes<-as.vector(unname(table(ice_cream_flavor)))
#建造函數
#1 sin函數
sin_df<-data.frame(x=c(pi,-pi))

ggplot(sin_df,aes(x=x))+stat_function(fun=sin,geom="line")

#2 自創函數
X_square<-function(x){
  return(x^2)
}
range<-data.frame(x=c(-3,3))
ggplot(range,aes(x=x))+stat_function(fun=X_square,geom="line")

#如何排版圖片
library(ggplot2)

library(gridExtra)

plot1<-ggplot(iris, aes(x=Species, y=Sepal.Length))+
  geom_boxplot()
plot2<-ggplot(iris, aes(x=Species, y=Sepal.Width))+
  geom_boxplot()
plot3<-ggplot(iris, aes(x=Species, y=Petal.Length))+
  geom_boxplot()
plot4<-ggplot(iris, aes(x=Species, y=Petal.Width))+
  geom_boxplot()
grid.arrange(plot1, plot2, plot3, plot4, nrow=2, ncol=2)

```






























